# 线性混合效应模型 {#chap-linear-mixed-effects-models}

`?nlme::lme`

[Eugene Demidenko](https://www.eugened.org/) 的书《Mixed Models: Theory and Applications with R》[@Demidenko_2013_Mixed] 内容相当完整 <https://github.com/eugenedemidenko>

线性混合效应模型（Linear Mixed Models or Linear Mixed-Effects Models，简称 LME 或 LMM[^lin-meimei]）

[lme4](https://github.com/lme4/lme4/)

[robustlmm](https://github.com/kollerma/robustlmm)

线性混合效应模型 `nlme::lme` 和 `lme4::lmer` <https://rpsychologist.com/r-guide-longitudinal-lme-lmer>

贝叶斯线性混合效应模型 [blme](https://github.com/vdorie/blme) 提供 blmer 和 bglmer 两个函数



极大似然估计到限制极大似然估计的重大跨越 [@Bartlett_1937_Properties]

线性混合效应模型有时也称方差分量模型 

[ggeffects](https://github.com/strengejacke/ggeffects) 提供函数 `ggpredict` 和 `ggeffect` 用来绘制各种混合效应模型的边际效应 Marginal Effects 图

[ggPMX](https://github.com/ggPMXdevelopment/ggPMX) 混合效应模型诊断图

[^lin-meimei]: 杨灿老师给她起了一个美丽的中文名：林妹妹。参考他给统计之都的文章 [昔日因，今日意](https://cosx.org/2014/04/lmm-and-me)


> I think that the formula language does allow expressions with '/' to represent nested factors but I can't check right now as there is a fire in the building where my office is located. I prefer to simply write nested factors as `factor1 + factor1:factor2`.
>
>   --- Douglas Bates [^DB-help-2013]

[^DB-help-2013]: <https://stat.ethz.ch/pipermail/r-sig-mixed-models/2013q1/019945.html>


混合效应嵌套结构问题      

> I think what we are seeking is the marginal variance-covariance matrix of the parameter estimators (marginal with respect to the random effects random variable, B), which would have the form of the inverse of the crossproduct of a $(q+p)$ by $p$ matrix composed of the vertical concatenation of $-L^{-1}RZXRX^{-1}$ and $RX^{-1}$. (Note: You do *not* want to calculate the first term by inverting $L$, use `solve(L, RZX, system = "L")` 
>
> - [...] don't even think about using `solve(L)` 
> 
> - don't!, don't!, don't!
> 
> - have I made myself clear?
> 
> - don't do that (and we all know that someone will do exactly that for a very large $L$ and then send out messages about "R is SOOOOO SLOOOOW!!!!" :-) )
>
> --- Douglas Bates [^DB-help-2010]

[^DB-help-2010]: <https://stat.ethz.ch/pipermail/r-sig-mixed-models/2010q2/003615.html>


本节介绍 `MASS::glmmPQL`、 `nlme::lme`、`lme4::lmer` 和 `brms::brm` 求解线性混合效应模型的区别和联系

线性混合效应模型有多个化身，比如生态学里的分层线性模型（Hierarchical linear Model，简称 HLM）心理学的多水平线性模型（Multilevel Linear Model）。模型名称的多样性正说明它应用的广泛性！ 

下面以 sleepstudy 数据集为例介绍不同 R 包求解线性混合效应模型的过程

```{r sleepstudy}
# 加载数据集
data(sleepstudy, package = "lme4")
```

介绍数据集各个字段的含义

## MASS

```{r lmm-sleepstudy}
fit_lmm_mass <- MASS::glmmPQL(Reaction ~ Days,
  random = ~ Days | Subject, verbose = FALSE,
  data = sleepstudy, family = gaussian
)
```

介绍模型各个成分的含义，下面的随机效应形式如何编码成上述相关形式，random 的公式含义是？

```{r lmm-sleepstudy-summary}
summary(fit_lmm_mass)
```

介绍模型输出结果的解读

```{r tidy-lmm-output}
coef(summary(fit_lmm_mass))
```

## nlme

nlme 包

```{r fit-lmm-nlme}
fit_lmm_nlme <- nlme::lme(Reaction ~ Days,
  random = ~ Days | Subject, data = sleepstudy
)
summary(fit_lmm_nlme)
```

下面各个代码对应的模型是什么

```{r fit-lmm-gls}
fit.gls1 <- nlme::gls(Reaction ~ Days + Subject, data = sleepstudy)
fit.gls2 <- nlme::gls(Reaction ~ Days,
  weights = nlme::varIdent(form = ~Subject), data = sleepstudy
)
fit.gls3 <- nlme::gls(Reaction ~ Days,
  correlation = nlme::corCompSymm(form = ~ Days | Subject), 
  data = sleepstudy
)
summary(fit.gls3)
```

`nlme::gls` 以广义最小二乘拟合线性模型，误差可以具有相关性和异方差性，误差可以相关的，那么误差也可看作随机效应，是 REML 吗？选模型自然是对数似然 logLik 越大越好， AIC/BIC 越小越好？weights 的含义是各个组的方差是不是假定相同，或者具有何种关系？

## lme4

```{r fit-lmm-lme4}
fit_lmm_lme4 <- lme4::lmer(Reaction ~ Days + (Days | Subject), data = sleepstudy)
summary(fit_lmm_lme4)
```

## brms

> I've been reading Data Analysis Using Regression and Multilevel/Hierarchical Models by Gelman and Hill. I'm getting acquainted with my new cartoon character friends Elmer (lmer) and Bugs, and at some point it may become clear what is going on. At the moment though, the whole thing seems a bit Looney Tunes.
> 
>   --- Paul Miller [^PM-help-2011]

[^PM-help-2011]: <https://stat.ethz.ch/pipermail/r-sig-mixed-models/2011q3/016741.html>

brms 从贝叶斯的角度

```{r fit-lmm-brms}
library(Rcpp) # 从命名空间导入 brm 需要显式地加载 Rcpp 包
fit_lmm_brms <- brms::brm(Reaction ~ Days + (Days | Subject),
  data = sleepstudy, refresh = 0
)
summary(fit_lmm_brms)
```
