---
title: "beamer 中文幻灯片"
author:
  - 张三
  - 李四
date: "`r format(Sys.time(), '%Y年%m月%d日')`"
institute: "XX 大学，XX 学院，XX 系"
documentclass: ctexbeamer
output: 
  beamer_presentation: 
    citation_package: natbib
    theme: Cuerna
    fonttheme: structurebold
    colortheme:  default # brick
    keep_tex: no
    latex_engine: xelatex
    toc: no
    slide_level: 2
    template: null
classoption: "fontset=adobe,zihao=false"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## 设置字体 {#sec-setup-cuerna}

```r
tinytex::tlmgr_install(c('beamertheme-cuerna', 'textpos'))
```
