---
title: "beamer 中文幻灯片"
author:
  - 张三
  - 李四
date: "最近一次编译时间 `r format(Sys.time(), '%Y年%m月%d日%H时%M分%S秒')`"
institute: "XX 大学，XX 学院，XX 系"
documentclass: ctexbeamer
output: 
  bookdown::pdf_book: 
    base_format: rmarkdown::beamer_presentation
    toc: no
    latex_engine: xelatex
    citation_package: natbib
    template: null
    dev: "cairo_pdf"
header-includes:
    - \usepackage{pifont}
    - \usepackage{iitem}
    - \setbeamertemplate{itemize item}{\ding{47}}
    - \setbeamertemplate{itemize subitem}{\ding{46}}
    - \usecolortheme[named=RoyalBlue]{structure}
classoption: "fontset=adobe,zihao=false"
biblio-style: plainnat
natbiboptions: "authoryear,round"
link-citations: yes
section-titles: false
colorlinks: yes
linkcolor: RoyalBlue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# R 语言

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

