---
title: "标题"
subtitle: "副标题"
keywords: "关键词"
author: |
  | xx
  | 2018年5月27日
documentclass: ctexbeamer
output: 
  beamer_presentation: 
    citation_package: natbib
    theme: fibeamer
    fonttheme: structurebold
    keep_tex: no
    latex_engine: xelatex
    toc: no
    slide_level: 2
    template: null
header-includes:
    - \usepackage{pifont}
    - \usepackage{iitem}
    - \setbeamertemplate{itemize item}{\ding{47}}
    - \setbeamertemplate{itemize subitem}{\ding{46}}
section-titles: false
aspectratio: 43
classoption: "dvipsnames,UTF8,fontset=adobe,zihao=false"
themeoptions: 
  - faculty=phil
bibliography: 
 - packages.bib
biblio-style: apalike
biblio-title: 参考文献
link-citations: yes
colorlinks: yes
linkcolor: RoyalBlue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see [@rmarkdown2018].

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## fibeamer 主题

[fibeamer](https://github.com/Witiko/fibeamer) 为不同的学院设计了不同颜色主题 fi / sci / law / econ/ fss/ med/ ped / phil /fsps

```bash
tlmgr install carlito
```

作者目前推荐使用 [mubeamer](https://www.fi.muni.cz/lemma/projekty/mubeamer) 来替代 fibeamer，开发在 Gitlab 上 <https://gitlab.ics.muni.cz/409729/mubeamer> 目前还未发布在 CTAN 官网上

系统需要安装 DejaVu Sans Mono 字体

## 运行环境 {#session-info .allowframebreaks}


```{r, comment=NA}
xfun::session_info(packages = c("rmarkdown", "bookdown"), dependencies = FALSE)
```

```{r bib,include=FALSE,cache=FALSE}
# automatically create a bib database for R packages
bib <- knitr::write_bib(
  x = c(
    "rmarkdown"
  ), file = NULL, prefix = ""
)
bib <- unlist(bib)
xfun::write_utf8(bib, "packages.bib")
```
