---
title: "beamer 中文幻灯片"
author: "xx"
date: "xx"
institute: "XX 大学，XX 学院，XX 系"
documentclass: ctexbeamer
output: 
  bookdown::pdf_book: 
    base_format: rmarkdown::beamer_presentation
    toc: no
    keep_tex: no
    latex_engine: xelatex
    citation_package: natbib
    theme: focus # 主题
    template: null
    dev: "cairo_pdf"
    highlight: "pygments" # 代码高亮
    pandoc_args: !expr rmarkdown:::pandoc_lua_filters("latex-div.lua")
classoption: "fontset=adobe,zihao=false"
aspectratio: 1610
bibliography: 
 - packages.bib
biblio-style: plainnat
natbiboptions: "authoryear,round"
link-citations: yes
colorlinks: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



# Markdown
## R Markdown

This is an R Markdown presentation[@rmarkdown2018]. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <https://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## 自定义块


::: {.block data-latex=""}
文本
:::

. . .

::: {.exampleblock data-latex=""}
示例
:::

. . .

::: {.alertblock data-latex=""}
警告
:::


## Slide with Plot

```{r pressure,fig.width=6,fig.height=5,out.width="65%"}
plot(pressure, family = "Dejavu Sans")
```

## 安装主题

[focus](https://github.com/elauksap/focus-beamertheme) 主题已经发布在 CTAN 上 <https://ctan.org/pkg/beamertheme-focus>

```bash
tlmgr install beamertheme-focus appendixnumberbeamer fira
```

## Tables


Table: (\#tab:demo) Demonstration of simple table syntax.

  Right     Left     Center     Default
-------     ------ ----------   -------
     12     12        12            12
    123     123       123          123
      1     1          1             1

## Figures

![(\#fig:r-logo) Figure caption](`r knitr::fig_chunk('pressure', 'pdf')`){ width=50% }



## 致谢

Thanks for using **Focus**!

```{r bib,cache=FALSE}
# automatically create a bib database for R packages
bib <- knitr::write_bib(
  x = c(
    .packages(), "knitr", "rmarkdown", "bookdown"
  ), file = NULL, prefix = ""
)
xfun::write_utf8(unlist(bib), "packages.bib")
```
